### 2011-12-03 AffineLieAlgebras/Thesis/3.tex
More translations.

В случае инъективного сплинта второй стебель $\Delta _{\frak{s}}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (\ref{product}) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$. Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$. Верна следующая гипотеза.

\begin{Cnj}
Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
\begin{equation}
\prod_{\beta \in \Delta _{\frak{s}}^{+}}\left( 1-e^{-\beta }\right)
=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
\end{equation}
\end{Cnj}

@@

В этом разделе мы рассмотрим свойства инъективных сплинтов $\Delta \approx (\Delta _{\af},\Delta _{\frak{s}})$. Мы покажем, что в этом случае вычисление коэффициентов ветвления для расщепляющего вложения $\af\hookrightarrow\gf$ эквивалентно нахождению кратностей весов неприводимого $\frak{s}$-модуля $L_{\frak{s}}^{\nu }$ с определенным старшим весом $\nu $. Заметим, что алгебра $\frak{s}$ не обязательно должна быть подалгеброй $\gf$.

Let us return to relation (\ref{singular main}) and multiply both sides by $%
R_{\af}$:
\begin{equation}
\frac{1}{\prod_{\beta \in \Delta _{\frak{s}}^{+}}(1-e^{-\beta })}\Psi _{%
\gf}^{\left( \mu \right) }=\sum_{\nu \in P_{\af}^{+}}b_{\nu
}^{(\mu )}\Psi _{\af}^{\left( \nu \right) }.
\label{singular main-2}
\end{equation}
Here the first factor in the l.h.s. is the inverse of the fan $\Gamma _{%
\af\rightarrow \gf}$. Consider the highest weight module $L_{\frak{%
s}}^{\nu }$. The embedding $\phi :\Delta _{\frak{s}\,0}\longrightarrow \Delta
_{\gf}$ sends the singular element $\Psi _{\frak{s}}^{\left( \nu
\right) }$ into $\Psi _{\gf}^{\left( \mu \right) }$. Applying the
inverse morphism $\phi ^{-1}$ to the product $\left( \prod_{\beta \in \Delta
_{\frak{s}}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\frak{s}%
}^{\left( \nu \right) }\right) $ one gets the character of the module $L_{%
\frak{s}}^{\nu }$,

\begin{equation}
\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\frak{s}%
}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\frak{s}}^{\left( \nu \right)
}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\frak{s}0
}^{+}}(1-e^{-\beta })}\Psi _{\frak{s}}^{\left( \nu \right) }=\mathrm{ch}%
\left( L_{\frak{s}}^{\nu }\right) .  \label{inverse for stem}
\end{equation}
Our task is to prove that the singular element $\Psi _{\gf}^{\left( \mu
\right) }$ contains the element $\Psi _{\frak{s}}^{\left( \xi \right) }$ for
a module $L_{\frak{s}}^{\xi }$ uniquely defined by $L_{\gf}^{\mu }$ and
that the branching coefficients $b_{\nu }^{(\mu )}$ in the r.h.s. of (\ref
{singular main-2}) coincide with multiplicities $m_{\zeta }^{\left( \xi
\right) }$ of the corresponding weights in $\mathcal{N}_{\frak{s}}^{\xi }$ .

For a highest weight irreducible module $L_{\gf}^{\mu }$ the singular
element $\Psi _{\gf}^{\left( \mu \right) }$ is an element of $\mathcal{E%
}$ corresponding to the shifted Weyl-orbit of the weight $\left( \mu +\rho
\right) \in P^{+}$ with the sign function $\epsilon \left( w\right) $. It is
convenient to use also unshifted singular elements
\begin{equation}
\Phi ^{\left( \mu \right) }:=\Psi ^{\left( \mu \right) }e^{\rho }.
\label{definition Phi}
\end{equation}
In these terms the relation (\ref{singular main-2}) looks like
\begin{equation}
\frac{e^{\rho _{\gf}-\rho _{\af}}}{\prod_{\beta \in \Delta _{\frak{%
s}}^{+}}(1-e^{-\beta })}\Phi _{\gf}^{\left( \mu \right) }=\sum_{\nu \in
P_{\af}^{+}}b_{\nu }^{(\mu )}\Phi _{\af}^{\left( \nu \right) }.
\label{singular main-3}
\end{equation}
The orbit related to $\Phi _{\gf}^{\left( \mu \right) }$ is completely
defined by the set of edges $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$
adjusted to the end of the highest weight vector $\mu +\rho $. For $\mu
=\sum m_{i}\omega _{i}$ these edges are
\begin{equation}
\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i},\quad i=1,\dots ,r.
\label{edge}
\end{equation}
Each formal exponent $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\gf%
}^{\left( \mu \right) }$ bears the sign coefficient $\epsilon =(-)$. The
defining property of $\Phi _{\gf}^{\left( \mu \right) }$ is as follows.
Consider any pair of edges $\lambda _{i},\lambda _{j}$ and the corresponding
weights $\mu +\rho $, $\mu +\rho +\lambda _{i}$ and $\mu +\rho +\lambda _{j}$. 
Apply the reflection $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
\begin{equation}
s_{\alpha _{i}}\circ \left\{
\begin{array}{l}
\left( \mu +\rho \right)  \\
\left( \mu +\rho +\lambda _{i}\right)  \\
\left( \mu +\rho +\lambda _{j}\right)
\end{array}
\right. =\left\{
\begin{array}{l}
\left( \mu +\rho +\lambda _{i}\right)  \\
\left( \mu +\rho \right)  \\
\left( \mu +\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha
_{j}\right)
\end{array}
\right.   \label{reflected triple}
\end{equation}

\begin{Prop}
The edge $\lambda _{i,j}$ of $\Phi _{\gf}^{\left( \mu \right) }$
starting at the weight $\left( \mu +\rho +\lambda _{i}\right) $ along the
root $-s_{\alpha _{i}}\circ \alpha _{j}$ has the same length in $(s_{\alpha
_{i}}\circ \alpha _{j})$ as $\lambda _{j}$ has in $\alpha _{j}$. (The same
is true for the edge $\lambda _{j,i}$, its length in $(s_{\alpha _{j}}\circ
\alpha _{i})$ is equal to the length of $\lambda _{i}$ in $\alpha _{i}$.)
\label{diagram property}
\end{Prop}

In $\Phi _{\gf}^{\left( \mu \right) }$ the elements $e^{\left( \mu
+\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ and $%
e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha _{j}}\circ \alpha
_{i}\right) }$ have the sign coefficient  $\epsilon =(+)$.

Remember that only three types of splints are
injective and thus are naturally connected with branching. Below we
reproduce the part of the splints table from \cite{richter2008splints} corresponding to
injective splints:
\[
\begin{array}{cc||c|c}
\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
_{\af}\hspace{0.25in} & \hspace{0.25in}\Delta _{\frak{s}}\hspace{0.25in}
\\ \hline\hline
\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
& F_{4} & D_{4} & D_{4} \\ \hline
\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
^{r}A_{1} \\
& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
\end{array}
\]
Each row in the table gives a splint $(\Delta _{\af},\Delta _{\frak{s}})
$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
\af}$ and $\Delta _{\frak{s}}$ are embedded metrically. Stems in the
first type splints are equivalent and in the second are not. In the third
type splints only $\Delta _{\af}$ is embedded metrically. The summands $%
u\left( 1\right) $ are added to keep $r_{\af}=r$. This does not change
the principle properties of branching but makes it possible to use the
multiplicities of $\frak{s}$-modules without further projecting their
weights.

Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\frak{s}}$. 
It is easy to check that for any injective splint the subset $S_{%
\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
_{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
_{k}\in \Delta _{\frak{s}}$ and that the orbit corresponding to $\Phi _{%
\gf}^{\left( \mu \right) }$ contains the edges
\begin{equation}
\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge}
\end{equation}
attached to the weight $\mu +\rho $. As far as $\Delta _{\af}$ is a
root system and for any pair of simple roots from $S_{\frak{c}}$ the
property \ref{diagram property} is fulfilled, the element $\Phi _{\gf%
}^{\left( \mu \right) }$ being a singular element for a set of $\af$%
-modules. Consider $\beta _{l}\in \Delta _{\frak{s}}$ whose coimage in $%
\Delta _{\frak{s}0}$ is simple. In Appendix it is shown that for any such $%
\beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
$\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
corresponding edge intersects the boundary plane of the fundamental chamber $%
\bar{C_{\af}}$ orthogonal to the root $\alpha _{l}$,
\begin{equation}
s_{\alpha _{l}}\left( \mu +\rho -p\beta _{l}\right) =s_{\alpha _{l}}\left(
\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l},
\label{intersection}
\end{equation}
\begin{equation}
\mu +\rho -s_{\alpha _{l}}\left( \mu +\rho \right) =\left( m_{l}+1\right)
\alpha _{l}=\left( m_{l}+1\right) \beta _{l}-\left( m_{l}+1\right) \beta
_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}.  
\label{intersection-2}
\end{equation}
It follows that $p=\left( m_{l}+1\right) $ and $s_{\alpha _{l}}\beta
_{l}=\beta _{k}$. Now apply the operator $s_{\beta _{k}}$ and find that the
edge along the root $s_{\beta _{k}}\alpha _{l}$ attached at the weight $%
s_{\beta _{k}}(\mu +\rho )$ is also equal to $-ps_{\beta _{k}}\alpha _{l}$.
This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\frak{s}}$ the edges $\lambda
_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
m_{l}+1\right) \beta _{l}$ and $\lambda _{kl}=-\left( m_{l}+1\right)
s_{\beta _{k}}\alpha _{l}$ demonstrate the property \ref{diagram property}.
One can continue this procedure further in the 2-dimensional subspace fixed
by the roots $\beta _{k}$ and $\beta _{l}$ and find the set of formal
exponents that being supplied with the corresponding sign factors compose
the coimage of the singular element of a module for the subalgebra in $\frak{%
s}$ (this subalgebra has rank $r=2$).

The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
simple in $\Delta _{\frak{s}0}$ and correspondingly for any $r=2$ subalgebra
in $\frak{s}$. The latter means that to ''find'' a singular element of $%
\frak{s}$-module in $\Phi _{\gf}^{\left( \mu \right) }$ it is necessary
to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
-\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\frak{s}}^{%
\widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $%
, they have the same Dynkin numbers:
\begin{equation}
\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
m_{k}\widetilde{\omega }_{k} . \label{new h weight}
\end{equation}
The next step is to construct the full $W_{\frak{s}}$-orbit $\Phi _{\frak{s}%
}^{\left( \widetilde{\mu }\right) }$  in $P_{\frak{s}}$. It is easily seen
that its coimage belongs to $\bar{C_{\af}}$ and that the set $\phi
^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) \setminus \Phi _{%
\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ corresponds to the
weights belonging to the boundary $\bar{C_{\af}}$ (including the subset
$\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
the appropriate sign factors that after being added to $\Phi _{\gf%
}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ form the diagram $\phi
^{-1}\left( \Phi _{\frak{s}}^{\widetilde{\mu }}\right) $ in $\bar{C_{\af%
}}$.

>>>>

В случае инъективного сплинта второй стебель $\Delta _{\sfr}:=\Delta_{2}=\Delta \setminus \Delta _{\af}$ может быть переписан как произведение (\ref{product}) и определяет веер вложения  $\Gamma _{\af\hookrightarrow \gf}$. Обозначим через $\Delta_{\mathfrak{s}0}$ кообраз второго вложения $\phi:\Delta_{\mathfrak{s}0}\to \Delta_{\gf}$. Верна следующая гипотеза.

\begin{Cnj}
Каждый инъективный сплинт $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$ определяет веер вложения с носителем $\left\{ \xi \right\} _{\af\rightarrow \gf}$, задающимся произведением
\begin{equation}
\prod_{\beta \in \Delta _{\sfr}^{+}}\left( 1-e^{-\beta }\right)
=-\sum_{\gamma \in P}s(\gamma )e^{-\gamma }\quad   \label{splint product}
\end{equation}
\end{Cnj}

@@

В этом разделе мы рассмотрим свойства инъективных сплинтов $\Delta \approx (\Delta _{\af},\Delta _{\sfr})$. Мы покажем, что в этом случае вычисление коэффициентов ветвления для расщепляющего вложения $\af\hookrightarrow\gf$ эквивалентно нахождению кратностей весов неприводимого $\sfr$-модуля $L_{\sfr}^{\nu }$ с определенным старшим весом $\nu $. Заметим, что алгебра $\sfr$ не обязательно должна быть подалгеброй $\gf$.

Вернемся к соотношению  (\ref{singular main}) и домножим обе стороны на  $R_{\af}$:
\begin{equation}
\frac{1}{\prod_{\beta \in \Delta _{\sfr}^{+}}(1-e^{-\beta })}\Psi _{\gf}^{\left( \mu \right) }=\sum_{\nu \in P_{\af}^{+}}b_{\nu}^{(\mu )}\Psi _{\af}^{\left( \nu \right) }.
\label{singular main-2}
\end{equation}
Здесь первый множитель в левой части -- это формальный элемент, обратный к вееру $\Gamma _{\af\rightarrow \gf}$. Рассмотрим модуль старшего веса $L_{\sfr}^{\nu }$. Вложение $\phi :\Delta _{\sfr\,0}\longrightarrow \Delta_{\gf}$ переводит сингулярный элемент  $\Psi _{\sfr}^{\left( \nu\right) }$ в $\Psi _{\gf}^{\left( \mu \right) }$. Применяя обратный морфизм $\phi ^{-1}$ к произведению $\left( \prod_{\beta \in \Delta_{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}\phi \left( \Psi _{\sfr}^{\left( \nu \right) }\right) $, мы получаем характер модуля $L_{\sfr}^{\nu }$,

\begin{equation}
\phi ^{-1}\left( \frac{1}{\prod_{\beta \in \Delta _{\sfr%
}^{+}}(1-e^{-\beta })}\phi \left( \Psi _{\sfr}^{\left( \nu \right)
}\right) \right) =\frac{1}{\prod_{\beta \in \Delta _{\sfr0
}^{+}}(1-e^{-\beta })}\Psi _{\sfr}^{\left( \nu \right) }=\mathrm{ch}%
\left( L_{\sfr}^{\nu }\right) .  \label{inverse for stem}
\end{equation}
Наша задача состоит в том, чтобы доказать, что сингулярный элемент $\Psi _{\gf}^{\left(\mu\right) }$ содержит элемент $\Psi _{\sfr}^{\left( \xi \right) }$ для модуля $L_{\sfr}^{\xi }$, однозначно определяемого модулем $L_{\gf}^{\mu }$ и что коэффициенты ветвления $b_{\nu }^{(\mu )}$ в правой части равенства (\ref{singular main-2}) совпадают с кратностями $m_{\zeta }^{\left( \xi\right) }$ соответствующих весов в $\mathcal{N}_{\sfr}^{\xi }$ .

Для неприводимого модуля старшего веса $L_{\gf}^{\mu }$ сингулярный элемент $\Psi _{\gf}^{\left( \mu \right) }$ -- это элемент $\mathcal{E}$, соответствующий сдвинутой орбите группы веса $\left( \mu +\rho\right) \in P^{+}$, со знаковой функцией $\epsilon \left( w\right) $. Удобно использовать также не сдвинутые сингулярные элементы
\begin{equation}
\Phi ^{\left( \mu \right) }:=\Psi ^{\left( \mu \right) }e^{\rho }.
\label{definition Phi}
\end{equation}
В этих обозначениях соотношение (\ref{singular main-2}) имеет вид
\begin{equation}
\frac{e^{\rho _{\gf}-\rho _{\af}}}{\prod_{\beta \in \Delta _{\frak{%
s}}^{+}}(1-e^{-\beta })}\Phi _{\gf}^{\left( \mu \right) }=\sum_{\nu \in
P_{\af}^{+}}b_{\nu }^{(\mu )}\Phi _{\af}^{\left( \nu \right) }.
\label{singular main-3}
\end{equation}
Орбита, связанная с  $\Phi _{\gf}^{\left( \mu \right) }$, полностью определяется набором ребер $\left\{ \lambda _{i}\right\} _{i=1,\dots ,r}$ построенным из конца вектора старшего веса $\mu +\rho $. Для $\mu=\sum m_{i}\omega _{i}$ эти ребра равны
\begin{equation}
\lambda _{i}=-\left( m_{i}+1\right) \alpha _{i},\quad i=1,\dots ,r.
\label{edge}
\end{equation}
Каждая формальная экспонента $e^{\mu +\rho +\lambda _{i}}$ in $\Phi _{\gf}^{\left( \mu \right) }$ снабжена знаковым коэффициентом  $\epsilon =(-)$. Можно определить $\Phi_{\gf}^{\left( \mu \right) }$ следующим свойством. Рассмотрим любую пару ребер $\lambda _{i},\lambda _{j}$ и соответствующие веса $\mu +\rho $, $\mu +\rho +\lambda _{i}$ и $\mu +\rho +\lambda _{j}$. 
Применим отражение $s_{\alpha _{i}}$ (or $s_{\alpha _{j}}$),
\begin{equation}
s_{\alpha _{i}}\circ \left\{
\begin{array}{l}
\left( \mu +\rho \right)  \\
\left( \mu +\rho +\lambda _{i}\right)  \\
\left( \mu +\rho +\lambda _{j}\right)
\end{array}
\right. =\left\{
\begin{array}{l}
\left( \mu +\rho +\lambda _{i}\right)  \\
\left( \mu +\rho \right)  \\
\left( \mu +\rho +\lambda _{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha
_{j}\right)
\end{array}
\right.   \label{reflected triple}
\end{equation}

\begin{Prop}
Ребро  $\lambda _{i,j}$ сингулярного элемента $\Phi _{\gf}^{\left( \mu \right) }$, начинающееся в весе $\left( \mu +\rho +\lambda _{i}\right) $ и направленное вдоль корня $-s_{\alpha _{i}}\circ \alpha _{j}$ имеет такую же длину, выраженную в длинах корня $(s_{\alpha_{i}}\circ \alpha _{j})$, как и $\lambda _{j}$ в длинах $\alpha _{j}$. (Это же верно для ребра $\lambda _{j,i}$, его длина в единицах $(s_{\alpha _{j}}\circ\alpha _{i})$ равна длине $\lambda _{i}$ в единицах $\alpha _{i}$.)
\label{diagram property}
\end{Prop}

В $\Phi _{\gf}^{\left( \mu \right) }$ элементы $e^{\left( \mu+\rho +\lambda_{i}-(m_{j}+1)s_{\alpha _{i}}\circ \alpha _{j}\right) }$ и $e^{\left( \mu +\rho +\lambda _{j}-(m_{i}+1)s_{\alpha_{j}}\circ \alpha_{i}\right) }$ имеют знаковый коэффициент  $\epsilon =(+)$.

Вспомним, что только три типа сплинтов инъективны и имеют естественную связь с ветвлениями. Ниже мы приводим часть таблицы сплинтов из работы \cite{richter2008splints}, соответствующую инъективным сплинтам:
\[
\begin{array}{cc||c|c}
\hbox{type} & \hspace{0.25in}\Delta \hspace{0.25in} & \hspace{0.25in}\Delta
_{\af}\hspace{0.25in} & \hspace{0.25in}\Delta _{\sfr}\hspace{0.25in}
\\ \hline\hline
\hbox{(i)} & G_{2} & A_{2} & A_{2} \\
& F_{4} & D_{4} & D_{4} \\ \hline
\hbox{(ii)} & B_{r}(r\geq 2) & D_{r} & \oplus ^{r}A_{1} \\
& C_{r}(r\geq 3) & D_{r} & \oplus ^{r}A_{1} \\ \hline
\hbox{(iii)} & A_{r}(r\geq 2) & A_{r-1}\oplus u\left( 1\right)  & \oplus
^{r}A_{1} \\
& B_{2} & A_{1}\oplus u\left( 1\right)  & A_{2}
\end{array}
\]
Each row in the table gives a splint $(\Delta _{\af},\Delta _{\sfr})
$ of the simple root system $\Delta $. In the first two types both $\Delta _{%
\af}$ and $\Delta _{\sfr}$ are embedded metrically. Stems in the
first type splints are equivalent and in the second are not. In the third
type splints only $\Delta _{\af}$ is embedded metrically. The summands $%
u\left( 1\right) $ are added to keep $r_{\af}=r$. This does not change
the principle properties of branching but makes it possible to use the
multiplicities of $\sfr$-modules without further projecting their
weights.

Splints induce a decomposition of the set $S=S_{\frak{c}}\cup S_{\frak{d}}$
with $S_{\frak{c}}=S\cap S_{\af}$ and $S_{\frak{d}}=S\cap S_{\sfr}$. 
It is easy to check that for any injective splint the subset $S_{%
\frak{d}}$ is nonempty. It follows that in the set $\left\{ \lambda
_{i}\right\} _{i=1,\dots ,r}$ one can always find simple roots $\beta
_{k}\in \Delta _{\sfr}$ and that the orbit corresponding to $\Phi _{%
\gf}^{\left( \mu \right) }$ contains the edges
\begin{equation}
\lambda _{k}=-\left( m_{k}+1\right) \beta _{k}  \label{beta edge}
\end{equation}
attached to the weight $\mu +\rho $. As far as $\Delta _{\af}$ is a
root system and for any pair of simple roots from $S_{\frak{c}}$ the
property \ref{diagram property} is fulfilled, the element $\Phi _{\gf%
}^{\left( \mu \right) }$ being a singular element for a set of $\af$%
-modules. Consider $\beta _{l}\in \Delta _{\sfr}$ whose coimage in $%
\Delta _{\sfr0}$ is simple. In Appendix it is shown that for any such $%
\beta _{l}$ there exists a root $\alpha _{l}\in S_{\frak{c}}$ such that
$\beta _{l}=\alpha _{l}+\beta _{k}$. It is easily seen that the
corresponding edge intersects the boundary plane of the fundamental chamber $%
\bar{C_{\af}}$ orthogonal to the root $\alpha _{l}$,
\begin{equation}
s_{\alpha _{l}}\left( \mu +\rho -p\beta _{l}\right) =s_{\alpha _{l}}\left(
\mu +\rho \right) -ps_{\alpha _{l}}\beta _{l}=\mu +\rho -p\beta _{l},
\label{intersection}
\end{equation}
\begin{equation}
\mu +\rho -s_{\alpha _{l}}\left( \mu +\rho \right) =\left( m_{l}+1\right)
\alpha _{l}=\left( m_{l}+1\right) \beta _{l}-\left( m_{l}+1\right) \beta
_{k}=p\beta _{l}-ps_{\alpha _{l}}\beta _{l}.  
\label{intersection-2}
\end{equation}
It follows that $p=\left( m_{l}+1\right) $ and $s_{\alpha _{l}}\beta
_{l}=\beta _{k}$. Now apply the operator $s_{\beta _{k}}$ and find that the
edge along the root $s_{\beta _{k}}\alpha _{l}$ attached at the weight $%
s_{\beta _{k}}(\mu +\rho )$ is also equal to $-ps_{\beta _{k}}\alpha _{l}$.
This means that for the triple of roots $\beta _{k},\beta _{l}$ and $%
s_{\beta _{k}}\alpha _{l}$ in $\Delta _{\sfr}$ the edges $\lambda
_{k}=-\left( m_{k}+1\right) \beta _{k}$, $\lambda _{l}=-\left(
m_{l}+1\right) \beta _{l}$ and $\lambda _{kl}=-\left( m_{l}+1\right)
s_{\beta _{k}}\alpha _{l}$ demonstrate the property \ref{diagram property}.
One can continue this procedure further in the 2-dimensional subspace fixed
by the roots $\beta _{k}$ and $\beta _{l}$ and find the set of formal
exponents that being supplied with the corresponding sign factors compose
the coimage of the singular element of a module for the subalgebra in $\frak{%
s}$ (this subalgebra has rank $r=2$).

The same can be proven for any positive root $\beta _{l}\in \Delta $ that is
simple in $\Delta _{\sfr0}$ and correspondingly for any $r=2$ subalgebra
in $\sfr$. The latter means that to ''find'' a singular element of $%
\sfr$-module in $\Phi _{\gf}^{\left( \mu \right) }$ it is necessary
to incorporate in it additional formal elements $\left\{ -e^{\mu +\rho
-\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{\frak{c}}\right\}.$ This
fixes the starting edges of the diagram $\phi ^{-1}\left( \Phi _{\sfr}^{%
\widetilde{\mu }}\right) $. As it follows from the reconstruction procedure
the highest weight $\widetilde{\mu }$ is totally defined by the weight $\mu $%
, they have the same Dynkin numbers:
\begin{equation}
\mu =\sum m_{k}\omega _{k}\qquad \Longrightarrow \quad \widetilde{\mu }=\sum
m_{k}\widetilde{\omega }_{k} . \label{new h weight}
\end{equation}
The next step is to construct the full $W_{\sfr}$-orbit $\Phi _{\sfr%
}^{\left( \widetilde{\mu }\right) }$  in $P_{\sfr}$. It is easily seen
that its coimage belongs to $\bar{C_{\af}}$ and that the set $\phi
^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) \setminus \Phi _{%
\gf}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ corresponds to the
weights belonging to the boundary $\bar{C_{\af}}$ (including the subset
$\left\{ -e^{\mu +\rho -\left( m_{l}+1\right) \beta _{l}}|\beta _{l}\in S_{%
\frak{c}}\right\} $). Thus we have constructed all the formal elements\ with
the appropriate sign factors that after being added to $\Phi _{\gf%
}^{\left( \mu \right) }|_{\bar{C_{\af}}}$ form the diagram $\phi
^{-1}\left( \Phi _{\sfr}^{\widetilde{\mu }}\right) $ in $\bar{C_{\af%
}}$.

Now let us return to relation (\ref{singular main-3}). One can add to $%
\Phi _{\gf}^{\left( \mu \right) }$ pairs of formal elements
constructed above  with the opposite signs: $\epsilon \left( w\right)
|_{w\in W_{\sfr}}$ and $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$. 
Attribute the signs $\epsilon \left( w\right) |_{w\in W_{\sfr}}$ to
the elements whose weights we shall attribute to $\bar{C_{\af}}$. 
The same elements with the opposite signs are to be referred to the
neighboring Weyl chambers of $\bar{C_{\af}^{(l)}}$ (the latter are
connected with the main one via simple reflections $s_{\alpha _{l}}$ so the
signes $-\epsilon \left( w\right) |_{w\in W_{\sfr}}$ are natural for
them). In fact one can repeat the procedure and find additional singular
weights in any Weyl chamber $\bar{C_{\af}^{(m)}}$ and in them
additional singular weights always have the signs opposite to that in their
nearest neighbors. Thus without changing the element $\Phi _{\gf%
}^{\left( \mu \right) }$ one can present it as a sum
\begin{equation}
\Phi _{\gf}^{\left( \mu \right) }=\sum_{w\in W_{\af}}w\circ \left(
e^{\rho _{\af}}\Psi ^{\widetilde{\mu }+\rho _{\sfr}}\right)
\label{singular final}
\end{equation}
where the weight $\widetilde{\mu }=\sum m_{k}\omega _{\sfr}^{k}$ was
defined above. The decomposition (\ref{singular final}) provides the
possibility to apply the factor $\left( \prod_{\beta \in \Delta _{\sfr%
}^{+}}(1-e^{-\beta })\right) ^{-1}$ to each summand of the singular element $%
\Phi _{\gf}^{\left( \mu \right) }$ separately because the sets of
weights from different Weyl summands do not intersect. Taking into account
the isomorphism $\phi $ one can see that in the main Weyl chamber $\bar{C_{%
\af}}$ the set of weights generated by the factor $\left( \prod_{\beta
\in \Delta _{\sfr}^{+}}(1-e^{-\beta })\right) ^{-1}$ is isomorphic to
the weight diagram $\mathcal{N}_{\sfr}^{\widetilde{\mu }}$ of the $\frak{%
s}$-module $L_{\sfr}^{\widetilde{\mu }}$. Now one can restrict
relation (\ref{singular main-3}) to $\bar{C_{\af}}$ and obtain the main
result:
\begin{Prop}
\begin{equation}
\frac{e^{\rho _{\gf}}}{\prod_{\beta \in \Delta _{\sfr%
}^{+}}(1-e^{-\beta })}\left( \Psi ^{\widetilde{\mu }+\rho _{\sfr%
}}\right) =\sum_{\widetilde{\nu }\in \mathcal{N}_{\sfr}^{\widetilde{\mu }%
}}M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}e^{\left(
\mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}=\sum_{\nu \in P_{\af}^{++}}b_{\nu }^{(\mu )}e^{\nu }.
\label{singular main-4}
\end{equation}
Any weight with nonzero multiplicity in the r. h. s. is equal to one of the
highest weights in the decomposition. The multiplicity $M_{\left( \sfr%
\right) \widetilde{\nu }}^{\widetilde{\mu }}$ of the weight  $\widetilde{\nu
}\in \mathcal{N}_{\sfr}^{\widetilde{\mu }}$ defines the branching
coefficient $b_{\nu }^{(\mu )}$ for the highest weight $\nu =\left( \mu
-\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right) $:
\[
b_{\left( \mu -\phi \left( \widetilde{\mu }-\widetilde{\nu }\right) \right)
}^{(\mu )}=M_{\left( \sfr\right) \widetilde{\nu }}^{\widetilde{\mu }}.
\]
\end{Prop}
